---
title: "Towards confidence estimates in Cascade Networks using the SelectBoost package"
shorttitle: "SelectBoost: Confidence Estimates in Cascade Networks"
author: 
- name: "Frédéric Bertrand"
  affiliation: 
  - Université de Strasbourg and CNRS
  - IRMA, labex IRMIA
  email: frederic.bertrand@math.unistra.fr
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Towards confidence estimates in Cascade Networks using the SelectBoost package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

#Introduction

## Aims of the vignette
Extending results from the `Cascade` package: reverse engineering with selectboost to compute **confidence indices for a fitted model**. We first fit a model to a cascade network using the `Cascade` package `inference` function then we compute confidence indices for the inferred links using the `Selecboost` algorithm.

## References
* Reference for the Cascade modelling: Vallat, L., Kemper, C. a., Jung, N., Maumy-Bertrand, M., Bertrand, F., Meyer, N., Pocheville, A., Fisher, J. W., Gribben, J. G. et Bahram, S. (2013). Reverse-engineering the genetic circuitry of a cancer cell with predicted intervention in chronic lymphocytic leukemia. *Proceedings of the National Academy of Sciences of the United States of America*, 110(2), 459-64.

* Reference for the Cascade package: Jung, N., Bertrand, F., Bahram, S., Vallat, L. et Maumy-Bertrand, M. (2014). Cascade : A R package to study, predict and simulate the diffusion of a signal through a temporal gene network. *Bioinformatics*.

# Code
Code to reproduce the datasets saved with the package and some the figures of the article Aouadi et al. (2018), <arXiv:1810.01670>

## Data simulation
```{r Cascade, cache= FALSE}
library(Cascade)
```

We define the F array for the simulations.
```{r, cache= FALSE}
T<-4
F<-array(0,c(T-1,T-1,T*(T-1)/2))

for(i in 1:(T*(T-1)/2)){diag(F[,,i])<-1}
F[,,2]<-F[,,2]*0.2
F[2,1,2]<-1
F[3,2,2]<-1
F[,,4]<-F[,,2]*0.3
F[3,1,4]<-1
F[,,5]<-F[,,2]
```

We set the seed to make the results reproducible
```{r, cache= TRUE}
set.seed(1)
Net<-Cascade::network_random(
  nb=100,
  time_label=rep(1:4,each=25),
  exp=1,
  init=1,
  regul=round(rexp(100,1))+1,
  min_expr=0.1,
  max_expr=2,
  casc.level=0.4
)
Net@F<-F
```

We simulate gene expression according to the network Net
```{r message=FALSE, cache=}
M <- Cascade::gene_expr_simulation(
  network=Net,
  time_label=rep(1:4,each=25),
  subject=5,
  level_peak=200)
```

## Network inference
We infer the new network.
```{r, cache= TRUE, fig.keep='none'}
Net_inf_C <- Cascade::inference(M,cv.subjects=TRUE)
```

Heatmap of the coefficients of the Omega matrix of the network
```{r, cache= TRUE}
stats::heatmap(Net_inf_C@network, Rowv = NA, Colv = NA, scale="none", revC=TRUE)
```

```{r, cache= TRUE}
Fab_inf_C <- Net_inf_C@F
```

## Compute the confidence indices for the inference
```{r, cache= TRUE}
library(SelectBoost)
set.seed(1)
```

By default the crossvalidation is made subjectwise according to a leave one out scheme and the resampling analysis is made at the .95 `c0` level
```{r, cache= TRUE}
net_pct_selected <- selectboost(M, Fab_inf_C)
```
```{r, cache= TRUE}
net_pct_selected_.5 <- selectboost(M, Fab_inf_C, c0value = .5)
```
```{r, cache= TRUE}
net_pct_selected_thr <- selectboost(M, Fab_inf_C, group = group_func_1)
```

Use `cv.subject=FALSE` to use default crossvalidation
```{r, cache= TRUE}
net_pct_selected_cv <- selectboost(M, Fab_inf_C, cv.subject=FALSE)
```

## Analysis of the confidence indices
Use plot to display the result of the confidence analysis.
```{r, cache= TRUE}
plot(net_pct_selected)
```

```{r, cache= TRUE}
plot(net_pct_selected_.5)
```

```{r, cache= TRUE}
plot(net_pct_selected_thr)
```

```{r, cache= TRUE}
plot(net_pct_selected_cv)
```

Distribution of non-zero (absolute value > 1e-5) coefficients
```{r, cache= TRUE}
hist(Net_inf_C@network[abs(Net_inf_C@network)>1e-5])
```

Plot of confidence at .95 resampling level versus coefficient value for non-zero (absolute value > 1e-5) coefficients
```{r, cache= TRUE}
plot(Net_inf_C@network[abs(Net_inf_C@network)>1e-5],net_pct_selected@network.confidence[abs(Net_inf_C@network)>1e-5])
```

```{r, cache= TRUE}
hist(net_pct_selected@network.confidence[abs(Net_inf_C@network)>1e-5])
```

Plot of confidence at .5 resampling level versus coefficient value for non-zero (absolute value > 1e-5) coefficients
```{r, cache= TRUE}
plot(Net_inf_C@network[abs(Net_inf_C@network)>1e-5],net_pct_selected_.5@network.confidence[abs(Net_inf_C@network)>1e-5])
```

```{r, cache= TRUE}
hist(net_pct_selected_.5@network.confidence[abs(Net_inf_C@network)>1e-5])
```

Plot of confidence at .95 resamling level with groups created by thresholding the correlation matrix versus coefficient value for non-zero (absolute value > 1e-5) coefficients.
```{r, cache= TRUE}
plot(Net_inf_C@network[abs(Net_inf_C@network)>1e-5],net_pct_selected_thr@network.confidence[abs(Net_inf_C@network)>1e-5])
```

```{r, cache= TRUE}
hist(net_pct_selected_thr@network.confidence[abs(Net_inf_C@network)>1e-5])
```

Plot of confidence at .95 resampling level versus coefficient value for non-zero (absolute value > 1e-5) coefficients using standard cross-validation.
```{r, cache= TRUE}
plot(Net_inf_C@network[abs(Net_inf_C@network)>1e-5],net_pct_selected_cv@network.confidence[abs(Net_inf_C@network)>1e-5])
```

```{r, cache= TRUE}
hist(net_pct_selected_cv@network.confidence[abs(Net_inf_C@network)>1e-5])
```

## Further improvements
Either decrease percent selected or choose `c0` as a quantile.



